\clearpage

\vspace*{-0.2cm}
\thebibliography{12}

\bibitem{cousins}
Cousins, Robert D. and Highland, Virgil L., "Incorporating systematic 
uncertainties into an upper limit'', Nucl. Instrum. Meth. A320 331 (1992).

\bibitem{cls1}
T. Junk, ``Confidence level computation for combining searches with small statistics'', 
Nucl.Instrum.Meth. {\bf A434} (1999) 435–443, arXiv:hep-ex/9902006. 
doi:10.1016/S0168-9002(99)00498-2.

\bibitem{cls2}
A. L. Read, ``Modified frequentist analysis of search results (the CLs method)'', 
CERN Yellow Report CERN-2000-005 (2000) 81.

\bibitem{cls_lhc}
ATLAS Collaboration, CMS Collaboration, and LHC Higgs Combination Group, 
``Procedure for the LHC Higgs boson search combination in summer 2011'', (July, 2011)

\bibitem{bayesian}
A. O'Hagan and J.J. Forster, "Bayesian Inference'', Kendalls Advanced 
Theory of Statistics, Arnold, London 2B (2004).

\bibitem{rootstat}
L. Moneta et. {\it al.}, "The RooStats Project'', 
Proceedings of ACAT2010 conference (2010).

\bibitem{lands}
M. Chen, A. Korytov, "LandS: Limits and Signifcance'', 
{\small https://mschen.web.cern.ch/mschen/LandS/}, (2010)

\bibitem{hww_eps}
W.~Andrews, et al., "A Higgs Boson Search in the Fully Leptonic
$W^+W^-$ Final State'', CMS AN-2011/155 (2011).

\bibitem{hww_lp}
W.~Andrews, et al., "An Update of the search for the Higgs boson in
$\WW\to 2\ell 2\nu$ final state for the Lepton-Photon 2011 conference'',
CMS AN-2011/350 (2011).

\bibitem{LHCHiggsCrossSectionWorkingGroup:2011ti}
LHC Higgs Cross Section Working Group: S. Dittmaier, C. Mariotti, 
G. Passarino, R. Tanaka (Eds.) and others, "Handbook of LHC Higgs Cross 
Sections: Inclusive Observables", ArXiv: 1101.0593 (2011).

\bibitem{hzz}
W.~Andrews, et al., "A Higgs Boson Search in the $\ZZ\to 2\ell 2\nu$
Final State'', CMS AN-2011/155 (2011).


\bibitem{hzzlppas}
CMS Collaboration, "Search for the Higgs boson in the $H\to ZZ\to 2l2\nu$ 
channe in pp collisions at $\sqrt{s}$ = 7 TeV'', CMS PAS HIG-11-016.


