\begin{thebibliography}{99}                                                                                                                               
\bibitem{ref:atgc_theory}
  H.~Aihara {\it et al.}, ``Anomalous gauge boson interactions'',
  arXiv:hep-ph/9503425.
\bibitem{ref:atgc_method}
  P.~Adzik {\it et al.}, ``Towards a Measurement of pp->Zgamma and Study of Anomalous Trilinear Gauge Coupling Sensitivity with CMS in the Electron and Muon Channels'',
  CMS AN-2009/169
\bibitem{ref:wwnote} 
  W.~Andrews {\it et al.}, ``First Measurement of pp->WW Production Cross-Section at 7 TeV'',
  CMS AN-10-344

\bibitem{Chatrchyan:2011tz} 
  S.~Chatrchyan {\it et al.}  [CMS Collaboration], Phys.\ Lett.\ B {\bf 699}, 25 (2011) [arXiv:1102.5429 [hep-ex]].

\bibitem{ref:keys}
  K.~S.~Cranmer,``Kernel estimation in high-energy physics'',  Comput.\ Phys.\ Commun.\  {\bf 136} (2001) 198,  [arXiv:hep-ex/0011057].
\bibitem{ref:WWXS2011}
W.~Andrews {\it et al.}, ``Measurement of the WW Production Cross-section with the Full 2011 Dataset'',
CMS AN-12-061

%
% results from other experiments
%

% PDG
\bibitem{ref:pdg}
  K.~Nakamura {\it et al.}(Particle Data Group), J. Phys. G 37, 075021 (2010)

% d0 WW lnulnu
\bibitem{Abazov:2009ys} 
  V.~M.~Abazov {\it et al.}  [D0 Collaboration],
  ``Measurement of the WW production cross section with dilepton final states in p anti-p collisions at s**(1/2) = 1.96-TeV and limits on anomalous trilinear gauge couplings,''
  Phys.\ Rev.\ Lett.\  {\bf 103}, 191801 (2009)
  [arXiv:0904.0673 [hep-ex]].

% d0 lnujj
\bibitem{ref:atgc_d0}
  V.~M.~Abazov {\it et al.}  [D0 Collaboration], ``Measurement of trilinear gauge boson couplings from WW + WZ to lnu jj events in pp-bar collisions at sqrt{s}=1.96 TeV'',
  Phys.\ Rev.\  D {\bf 80}, 053012 (2009)

% ATLAS WW
\bibitem{} 
  G.~Aad {\it et al.}  [ATLAS Collaboration],
  ``Measurement of the WW cross section in sqrt(s) = 7 TeV pp collisions with the ATLAS detector and limits on anomalous gauge couplings,''
  arXiv:1203.6232 [hep-ex].

\end{thebibliography}


