The nonresonant $WW$ contribution in the signal region can be estimated from data 
using the dilepton invariant mass distribution. For a given Higgs boson mass, 
a $\ww$-dominated control region with a small contribution from Higgs decays 
can be selected. The $\ww$ contribution estimated in the control region 
is then extrapolated into the signal region using simulation. 

The control region can not be defined efficiently for $m_H>200\GeVcc$. Therefore for 
searches for a high mass Higgs we estimate the nonresonant 
$\ww$ contributions from simulation. 

For searches for low mass Higgs bosons with $m_{H}<200\GeVcc$, we define the $\ww$ control region as the events 
with $m_{\ell\ell} > 100~\GeVcc$ that pass the full event selection, except for the requirements on 
$m_T$ and $\Delta\phi$. This procedure has already been explained in detail in~\cite{HWW2011}, therefore only 
a brief summary is shown here:

\begin{itemize}
\item we first measure the yields in the control region in data; 
\item we then subtract the contamination from other backgrounds such as top and 
$\Wjets$, which can be estimated using corresponding data-driven techniques;
\item The resulting yield is subsequently extrapolated to the signal region, using 
the control-to-signal region ratio estimated from the dilepton invariant mass 
spectrum in simulation;
\item Finally, we multiply the yields in the signal region by the 
$m_T$ and $\Delta\phi_{ll}$ cut efficiency from simulation to get the 
$WW$ contribution in the signal region after all cuts.
\end{itemize}

\subsubsection{Theoretical Systematic Uncertainties} 
For Higgs mass hypothesis of $200\GeVcc$ and larger, there is significant signal contamination in 
the $WW$ control region as defined above. As a result, we use the prediction from the Monte Carlo
simulation with the full theoretical systematic uncertainty for the cross section and the 
jet bin migration. The jet bin migration uncertainty is primarily dominated by missing higher
order corrections in the prediction for the WW+1jet cross section. To evaluate this systematic 
uncertainty we estimate the uncertainty due to missing higher order corrections on the
total inclusive WW production cross section ($\sigma^{\mathrm{WW}}_{\geq 0}$) and the inclusive 
WW+1 or more jets cross section ($\sigma^{\mathrm{WW}}_{\geq 1}$), and propagating these uncertainties 
to the WW+1 jet cross section. To evaluate the uncertainty on 
$\sigma^{\mathrm{WW}}_{\geq 0}$, and $\sigma^{\mathrm{WW}}_{\geq 1}$ due to missing higher 
order corrections, we use MCFM \cite{MCFMVVProduction} to compute the inclusive cross sections, 
varying the renormalization and factorization scales. From these calculations we obtain 
systematic uncertainties on $\sigma^{\mathrm{WW}}_{\geq 0}$, and 
$\sigma^{\mathrm{WW}}_{\geq 1}$ of $\pm 3.4\%$ and $^{+15.2}_{-14.4} \%$ respectively. These are translated into
log normal representation as $\kappa^{\mathrm{WW}}_{\geq 0} = 1.034$ and $\kappa^{\mathrm{WW}}_{\geq 1} = 1.16$.

To propagate these uncertainties into uncertainties on the WW+1jet cross section, $\sigma^{\mathrm{WW}}_{1}$,
we evaluate the fraction of events in the 0-jet ($f_{0}$), 1-jet($f_{1}$), and 2-jet($f_{2}$) 
bins using the MCFM calculation and the Madgraph Monte Carlo simulation. The 0-jet fraction can be 
evaluated from the MCFM calculation via the relation 
$f_{0} = (\sigma^{\mathrm{WW}}_{\geq 0} - \sigma^{\mathrm{WW}}_{\geq 1}) / \sigma^{\mathrm{WW}}_{\geq 0}$.
Since we do not have a calculation of WW + 2 or more jets at next to leading order, the same calculation 
cannot be done for the  1jet fraction. Therefore, we use the Monte Carlo prediction and obtain 
$f_{1} = 0.19$ and $f_{2} = 0.05$. To propagate the effect of these uncertainties to the 
normalization of the 0-jet and 1-jet bins, we use the relations:

\begin{eqnarray}
\label{eqn:WWJetBinFractions}
\kappa^{\mathrm{0-jet}}_{\mathrm{QCDscale\_WW}} = (\kappa^{\mathrm{WW}}_{\geq 0})^{\frac{1}{f_{0}}},                 \\
\kappa^{\mathrm{0-jet}}_{\mathrm{QCDscale\_WW1in}} = (\kappa^{\mathrm{WW}}_{\geq 1})^{- \frac{f_{1}+f_{2}}{f_{0}}},  \\
\kappa^{\mathrm{1-jet}}_{\mathrm{QCDscale\_WW1in}} = (\kappa^{\mathrm{WW}}_{\geq 1})^{\frac{f_{1}+f_{2}}{f_{1}}},    \\
\end{eqnarray}

where $\kappa^{\mathrm{0-jet}}_{\mathrm{QCDscale\_WW}}$, $\kappa^{\mathrm{0-jet}}_{\mathrm{QCDscale\_WW1in}}$,
$\kappa^{\mathrm{1-jet}}_{\mathrm{QCDscale\_WW1in}}$, are the systematic uncertainties for the WW bkg normalization in 
the 0-jet bin due to missing higher order corrections in the inclusive WW cross section calculation,
for the WW background normalization in the 0-jet bin due to missing higher order corrections in the inclusive WW + 1 or 
more jet cross section calculation, and for the WW background normalization in the 1-jet bin due to missing higher 
order corrections in the inclusive WW + 1 or more jet cross section calculation, respectively. 
$\kappa^{\mathrm{0-jet}}_{\mathrm{QCDscale\_WW}} = 1.045$ and $\kappa^{\mathrm{0-jet}}_{\mathrm{QCDscale\_WW1in}} = 0.954$
are much smaller than the total systematic uncertainty from the data-driven estimate for the 0-jet bin and
therefore can be ignored. $\kappa^{\mathrm{1-jet}}_{\mathrm{QCDscale\_WW1in}}$ is $1.206$, corresponding to 
a $21\%$ systematic uncertainty on the normalization of the WW background in the 1-jet bin, and is propagated in the
analysis.
