
In this section we document the comparison of the documented EPS analysis results \cite{HZZ2011EPS, HZZ2011EPSPAS}
with those obtained applying the EPS high level analysis selections.  To do this we made the 
following modifications to our \zz~preselection as defined in Section \ref{sec:selection}:

\begin{itemize}
    \item Use \met~instead of the minimum of \met~and track \met.
    \item We modify the top veto to reject events with TCHE b-tag $<2.0$ only for counted jets.
\end{itemize}

We then applied the EPS analysis high level selections for the $m_{H}=300$~GeV analysis,
and compared these with those presented at the time of the approval of the EPS analysis.
In the case of our results, we applied the data driven background estimates and efficiency
correction factors as defined previously.
%Note that we did not apply any scaling to the signal MC to account for the missing VBF contribution, 
%which is done for the EPS results.
The selection requirements are:

\begin{itemize}
    \item $\met>82.9$~GeV.
    \item $242<m_{T}<320$~GeV.
    \item $\Delta\phi(\mathrm{\met, nearst jet}) > 0.28$.
\end{itemize}

The results are reported in Table \ref{tab:zzselection_all}.
No scaling is applied to the to the Crosscheck signal yields 
to take into account the missing VBF Monte Carlo.
We conclude that the results are consistent given the differences
in the low level event selections.  
This gives confidence in the robustness of the EPS results.

%%%%%%%%
\begin{table}[!ht]
\begin{center}
\begin{tabular} {c|c|c|c|cccc}
\hline
  & data & HZZ(300) & all bkg. & $\dyll$ & $\ZZ$ & $\WZ$ & $WW+\ttbar+tW+\Wjets$  \\
\hline
\multicolumn{8}{c} {EPS Analysis} \\
\hline
 $\mu\mu$ &  13 & $4.0 \pm 0.01$ & $15.0 \pm 1.8$ & $3.5 \pm 1.8$ & $5.2 \pm 0.13$  & $3.2 \pm 0.15$ & $3.0 \pm 1.3$ \\
 $ee$     &  21 & $3.1 \pm 0.01 $ & $11.0 \pm 1.3$ & $2.6 \pm 1.3$ & $3.8 \pm 0.12$  & $2.2 \pm 0.14$ & $2.2 \pm 1.0$ \\
\hline
\multicolumn{8}{c} {Crosscheck} \\
\hline
 $\mu\mu$ &  12 & $3.09 \pm 0.03$  & $16.84 \pm 1.07$ & $2.23 \pm 0.05$ & $5.11 \pm 0.17$ & $3.08 \pm 0.20$ & $6.41 \pm 1.0$  \\
 $ee$     &  18 & $2.20 \pm 0.03$  & $11.02 \pm 0.68$ & $2.23 \pm 0.05$ & $3.66 \pm 0.14$ & $1.86 \pm 0.15$ & $3.27 \pm 0.65$  \\
\hline
\end{tabular}
\caption{Expected number of signal and background events from the data-driven methods for an
  integrated luminosity of \intlumi  after applying the $\ZZ$ selection requirements.
Only statistical uncertaities are reported for the crosscheck. }
   \label{tab:zzselection_all}
  \end{center}
\end{table}
%%%%%%%%

