
\clearpage

\vspace*{-0.2cm}
\thebibliography{12}

\bibitem{ref:HiggsMechanism}
 P.~W.~Higgs, Phys.~Lett., {\bf 12}, 132 (1964).

\bibitem{ref:HiggsMechanism1}
 F.~Englert, Phys.~Rev.~Lett., {\bf 13}, 321 (1964).

\bibitem{ref:GlobalEwkConstraints}
ALEPH, CDF, D0, DELPHI, L3, OPAL, SLD, the LEP Electroweak Working Group, 
the Tevatron Electroweak Working Group, and the SLD Electroweak and Heavy Flavor Working Groups, ``Precision Electroweak 
Measurements and Constraints on the Standard Model'' arXiv:hep-ex/0911.2604.

\bibitem{ref:LepExclusion}
The ALEPH, DELPHI, L3 and OPAL Collaborations, and the LEP Working Group for Higgs boson searches,
Phys.~Lett.~B, 565, 61 (2003).

\bibitem{ref:TevExclusion}
CDF Collaboration and D0 Collaboration and Tevatron New Physics and Higgs Working Group, 
``Combined CDF and D0 upper limits on standard model higgs boson production with up to 6.7 fb$^{-1}$ of data'', arXiv:hep-ex/1007.4587v1.

\bibitem{ref:GF1}
D.~de~Florian and M.~Grazzini, Phys. Lett. {\bf B674}, 291 (2009).

\bibitem{ref:GF2}
C.~Anastasiou, R.~Boughezal, and F.~Petriello, J.~High~Energy~Phys. 04, 003 (2009).

\bibitem{ref:VBF}
E.~L.~Berger and J.~M.~Campbell, Phys. Rev. {\bf D70}, 073011 (2004).

\bibitem{ref:VH1}
O.~Brein, A.~Djouadi, and R.~Harlander, Phys. Lett. {\bf B579}, 149 (2004).

\bibitem{ref:VH2}
M.~L.~Ciccolini, S.~Dittmaier, and M.~Kramer, Phys. Rev. {\bf D68}, 073003 (2003).

\bibitem{ref:Hdecay}
A.~Djouadi, J.~Kalinowski, and M.~Spira, Comput. Phys.Commun. 108, 56 (1998).

\bibitem{ref:HWW2011smurf}
L.~Bauerdick, \textit{et al.}, ``A Higgs Boson Search in the Fully Leptonic $W^{+}W^{-}$ Final State'', CMS AN-2011/155.

\bibitem{ref:HZZ2011smurf}
L.~Bauerdick, \textit{et al.}, ``A Higgs Boson Search in the $ZZ \to 2\ell2\nu$ Final State'', CMS AN-2011/329.

\bibitem{ref:ShapeSmurf}
L.~Bauerdick, \textit{et al.}, ``Shape analysis for Higgs searches in di-lepton final state'', CMS AN-2011/???.

\bibitem{ref:CDFTopMass}
T.~Aaltonen {\it et al.} (CDF Collaboration),  Phys.\ Rev.\  {\bf D79}, 072010 (2009).

\bibitem{ref:D0TopMass}
V.~M.~Abazov {\it et al.} ( D0 Collaboration ), Phys.\ Rev.\  {\bf D74}, 092005 (2006).

\bibitem{ref:CDFDiboson}
T.~Aaltonen {\it et al.} ( CDF Collaboration ), Phys.\ Rev.\  {\bf D82}, 112001 (2010).

\bibitem{ref:CDFSingleTop}
T.~Aaltonen {\it et al.} ( CDF Collaboration ), Phys.\ Rev.\  {\bf D82}, 112005 (2010).

\bibitem{ref:D0SingleTop}
V.~M.~Abazov {\it et al.} ( D0 Collaboration ), Phys.\ Rev.\ Lett.\  {\bf 103}, 092001 (2009).

\bibitem{ref:CDFHiggs}
T.~Aaltonen {\it et al.} ( CDF Collaboration ), Phys. Rev. {\bf D80}, 071101 (2009). 

T.~Aaltonen {\it et al.} ( CDF Collaboration ), Phys. Rev. Lett. 103, 101802 (2009).

T.~Aaltonen {\it et al.} ( CDF Collaboration ), Phys. Rev. Lett. 102, 021802 (2009).

\bibitem{ref:D0Higgs}
V.~M.~Abazov {\it et al.} ( D0 Collaboration ), Phys. Rev. Lett. 102 (2009)

V.~M.~Abazov {\it et al.} ( D0 Collaboration ), Phys. Lett. B 663 (2009) 26.

\bibitem{ref:PDG}
Particle~Data~Group, http://pdg.lbnl.gov.

\bibitem{lands}
Mingshui Chen and Andrey Korytov, https://mschen.web.cern.ch/mschen/lands/

