\documentclass{cmspaper}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage[pdfborder=0 0 0,
            colorlinks,
            urlcolor = blue,
            linkcolor = black,
            citecolor = black,
            menucolor = black,]
           {hyperref}
%% \usepackage[colorlinks]{hyperref}
%% \usepackage{url}
\usepackage[toc,page]{appendix}
\renewcommand{\appendixname}{Appendix}
%% \renewcommand{\appendixtocname}{List of appendices}

% \input{privsym}
\input{commands}
\newcommand{\met}{\mbox{$E_T\hspace{-1.1em}/$\hspace{0.7em}}}

\setcounter{topnumber}{1}
\setcounter{bottomnumber}{1}


\begin{document}
\begin{titlepage}

\analysisnote{2011/489}

\date{\today}

\title{Matrix Element based searches for Standard Model Higgs boson in di-lepton final states with Full 2011 dataset.}

\input{Authlist}

\begin{abstract}
In this note we present searches for the standard model Higgs boson in the $WW \rightarrow l^{+}l^{-}\nu\bar{\nu}$ and $ZZ \rightarrow l^{+}l^{-}\nu\bar{\nu}$ 
final states. To achieve improved sensitivity compared to a cut-based approach, we use event probabilities based on Standard Model matrix elements to construct a likelihood function of the Higgs content of the data sample. The $H\rightarrow WW$ and $H\rightarrow ZZ$ analyses are performed using data sample corresponding to an integrated luminosity of 4.7 $fb^{-1}$  from $pp$ collisions at $\sqrt{s}=7$ TeV.
Events are required to have two reconstructed leptons, muons or electrons. For the $H\rightarrow WW$ search we compare the performance of the 
Matrix Element method to cut-based and Boosted Decision Tree based approaches. For the $H\rightarrow ZZ$ search we compare its performance to cut-and-count analysis and $m_{T}$ shape based one. We demonstrate that, with all systematic uncertainties taken into account, use of the matrix element method leads to a $15-30 \%$ improvement in the sensitivity when compared to cut-and-count based approach in both analyses. When compared to other shape analyses, it gives performance similar to that of the BDT in $H\rightarrow WW$, and performs 10\% better than $m_{T}$ at 250-300 GeV Higgs mass in $H\rightarrow ZZ$, with equal to $m_{T}$ performance at higher masses. Overall, using full 2011 4.7 $fb^{-1}$ data sample, we exclude Standard Model Higgs boson with mass 128--270 GeV (in $H\rightarrow WW$) and 310--500 GeV (in $H\rightarrow ZZ$) at 95\% C.L. 
\end{abstract}

%\maketitle

\end{titlepage}
\tableofcontents
%\listoftables
%\listoffigures
\newpage 

% body of paper here - Use proper section commands
% References should be done using the \cite, \ref, and \label commands

\section{Introduction}
\label{sec:Intro}
\input{meintro}


\section{$H \rightarrow WW$ }

\subsection{Method Overview}
\label{sec:Meth_Overview}
\label{hwwintro}

\subsection{Event Probability}
\label{sec:Evt_Prob}
\input{eventprob}


\subsection{Results}
\label{results_hww}
\input{results_hww_5fb}

\clearpage

\section{$H \rightarrow ZZ$ }
\label{sec:hzzintro}


\subsection{$Z$+jet background}
\label{sec:hzzbkg_zjets}
\input{hzzbkg_zjets}

\subsection{Validation using $WZ+ZZ$ Cross-section Measurement}
\label{sec:vzvalidation}
\input{vzvalidation}


\subsection{Results}
\label{sec:results_hzz}
\input{results_hzz_5fb}
\clearpage


\section{Summary}
\label{sec:summary}
\input{summary}

\clearpage

\appendix


 \section{$H\to WW$ expected and observed upper limits by sub-channels}
     \label{app:hwwsubchannels}
     \input{appendix_hww_subchannels}



\input{biblio} 




\end{document}
