\clearpage

\vspace*{-0.2cm}
\thebibliography{12}

\bibitem{discovery-atlas} 
ATLAS collaboration, Phys. Lett. B  {\bf 716}, 1 (2012).
%submitted to Phys. Lett. B, arXiv:1207.7214 [hep-ex].

\bibitem{discovery-cms} 
CMS collaboration, Phys. Lett. B {\bf 716}, 30 (2012).
%submitted to Phys. Lett. B, arXiv:1207.7235 [hep-ex].

%\bibitem{evidence-tev}
%CDF and D0 collaborations, Phys. Rev. Lett.  {\bf 109}, 071804 (2012).


\bibitem{Higgs1}
F. Englert and R. Brout, ``Broken symmetries and the masses of gauge bosons", Phys. Rev. Lett. 13,  1964.

\bibitem{Higgs2}
P. W. Higgs, ``Broken symmetry and the mass of gauge vector mesons", Phys. Rev. Lett. 13, 1964.

\bibitem{Higgs3}
Guralnik, G.S. and Hagen, C.R. and Kibble, T.W.B., ``Global Conservation Laws and Massless Particles", 
Phys.Rev.Lett. 13, 1964.

\bibitem{Ellis2012}
J. Ellis and D. S. Hwang, ``Does the `Higgs' have Spin Zero?'', JHEP {\bf 09}, 071 (2012). 
%to appear in JHEP, arXiv:1202.6660 [hep-ph].
%DOI: 10.1007/JHEP09(2012)071 

\bibitem{xww}
S. Bolognesi, Y. Gao, A. V. Gritsan et al, ``On the spin and parity of a single-produced resonance at the LHC'', arXiv:1208.4018

%\bibitem{dittmar}
%M.~Dittmar and H.~K.~Dreiner, Phys.\ Rev.\  D {\bf 55} (1997) 167".

\bibitem{HWWHCP2012}
W.~Andrews, et al., ``A Higgs Boson Search in the Fully Leptonic $W^+W^-$ Final State udpated for HCP2012 Conference'', CMS AN-2012/386 (2012).

\bibitem{jhugen}
S. Bolognesi, Y. Gao, A. V. Gritsan et al, http://www.pha.jhu.edu/spin/

\bibitem{powheg} 
S. Frixione and P. Nason and C. Oleari, 
``Matching {NLO QCD} computations with parton shower simulations: the {POWHEG} method",
  JHEP 11 070 (2007)

\bibitem{lands}
Mingshui Chen and Andrey Korytov, https://mschen.web.cern.ch/mschen/lands/.

%\bibitem{MCFMHiggsProduction}
%J. Campbell, R.K. Ellis, G. Zanderighi, ``Next-to-Leading order Higgs + 2 jet production via gluon fusion.'', JHEP 0610:028 (2006), hep-ph/0608194.

%\bibitem{MCFMVVProduction}
%J. Campbell, R.K. Ellis, C. Williams, ``Vector boson pair production at the LHC.'', arxiv:hep-ph/1105.0020.

\bibitem{MVASyst}
W. Andrews {\it et. al.}, ``Shape analysis for Higgs searches in di-lepton final state", 
CMS AN2011/408.

%\bibitem{wgstar}
%  R.~C.~Gray, C.~Kilic, M.~Park, S.~Somalwar and S.~Thomas,
%  ``Backgrounds To Higgs Boson Searches from Asymmetric Internal Conversion'',
%  arXiv:1110.1368 [hep-ph].

\bibitem{rootstat}
L. Moneta et. {\it al.}, ``The RooStats Project", Proceedings of ACAT2010 conference, 2010.

\bibitem{cls1}
T. Junk, ``Confidence level computation for combining searches with small statistics'', 
Nucl.Instrum.Meth. {\bf A434} (1999) 435–443, arXiv:hep-ex/9902006. 
doi:10.1016/S0168-9002(99)00498-2.

\bibitem{cls2}
A. L. Read, ``Modified frequentist analysis of search results (the CLs method)'', 
CERN Yellow Report CERN-2000-005 (2000) 81.

\bibitem{cls_lhc}
ATLAS Collaboration, CMS Collaboration, and LHC Higgs Combination Group, 
``Procedure for the LHC Higgs boson search combination in summer 2011'', (July, 2011)

%\bibitem{2DNote}
%L.~Bauerdick, et al., {A 2-dimensional Shape Analysis for the Higgs Boson Search in the Fully Leptonic \WW Final State}, CMS AN-2012/369 (2012).
