\clearpage

\vspace*{-0.2cm}
\thebibliography{12}

\bibitem{pdg}
 K. Nakamura et al. (Particle Data Group), ``Review of particle physics", J. Phys.G37 , 2010.

\bibitem{Higgs1}
F. Englert and R. Brout, ``Broken symmetries and the masses of gauge bosons", Phys. Rev. Lett. 13,  1964.

\bibitem{Higgs2}
P. W. Higgs, ``Broken symmetry and the mass of gauge vector mesons", Phys. Rev. Lett. 13, 1964.

\bibitem{Higgs3}
Guralnik, G.S. and Hagen, C.R. and Kibble, T.W.B., ``Global Conservation Laws and Massless Particles", 
Phys.Rev.Lett. 13, 1964.

\bibitem{dittmar}
M.~Dittmar and H.~K.~Dreiner, Phys.\ Rev.\  D {\bf 55} (1997) 167".

\bibitem{lephiggs}
ALEPH, DELPHI, L3, OPAL Collaborations, and the LEP Working Group 
for Higgs Boson Searches, ``Search for the Standard Model Higgs Boson at LEP''
, Phys. Lett. B{\bf 565} (2003) 61.

\bibitem{tevhiggs}
CDF and D0 Collaboration, ``Evidence for a particle produced in association 
with weak bosons and decaying into a bottom-antibottom quark pair 
in Higgs boson searches at the Tevatron'', Phys. Rev. Lett. {\bf 109} 
(2012), 071804. 

\bibitem{atlasdiscovery}
ATLAS Collaboration, ``Observation of a new particle in the search for 
the Standard Model Higgs boson with the ATLAS detector at the LHC'', 
Phys. Lett. B{\bf 716} (2012) 1-29. 

\bibitem{cmsdiscovery}
CMS Collaboration, ``Observation of a new boson at a mass of 125 GeV with 
the CMS experiment at the LHC'', Phys. Lett. B{\bf 716} (2012) 30-61. 

\bibitem{hwwhcp2012pas}
CMS Collaboration, ``Evidence for a particle decaying to $W^+W^-$ in 
the fully leptonic final state in a standard model Higgs boson search in 
pp collisions at the LHC'', CMS PAS HIG-042. 

\bibitem{hwwspinpaper}
S.~Bolongnesi, et al., ``On the spin and parity of a single-produced 
resonance at the LHC'', Phys. Rev. D {\bf 86} (2012), 095031. 

\bibitem{YY2DTalk}
Y.~Gao, et al., Review of the 2D Analysis in H->WW->lnln channel,
https://indico.cern.ch/getFile.py/access?contribId=38\&sessionId=7\&resId=0\&materialId=slides\&confId=211940.

\bibitem{ggWWError}
F.~ Stoeckli, ``http://indico.cern.ch/getFile.py/access?contribId=0\&resId=1\&materialId=slides\&confId=49009", 
EWK Diboson meeting of March 12 2009.

\bibitem{powheg} 
S. Frixione and P. Nason and C. Oleari, 
``Matching {NLO QCD} computations with parton shower simulations: the {POWHEG} method",
  JHEP 11 070 (2007)

\bibitem{json}
http://ceballos.web.cern.ch/ceballos/hwwlnln/merged\_r12.json

\bibitem{EGammaMvaId} 
https://twiki.cern.ch/twiki/bin/view/CMS/MultivariateElectronIdentification

\bibitem{ElIso}
A. Vartak, M. LeBourgeois, V. Sharma, ``Lepton Isolation in the CMS Tracker, ECAL and HCAL", CMS AN-2010/106.

\bibitem{MVAElId}
S.~Xie, \textit{et al.}, ``Electron Identification Using Multivariate Methods", 
CMS AN-2011/413.

\bibitem{MuonRingIso}
https://twiki.cern.ch/twiki/bin/view/CMS/MultivariateMuonSelection

\bibitem{PVDA}
W. Erdmann, M. LeBourgeois, B. Mangano, 
https://indico.cern.ch/getFile.py/access?contribId=5\&sessionId=3\&resId=1\&materialId=slides\&confId=127127, 
note in preparation.

\bibitem{NExpHits}
B. Mangano \textit{et al.}, ``Improvement in Photon Conversion Rejection Performance Using 
Advanced Tracking Tools", AN-10-283.

\bibitem{fakeLeptonNote1}
S.~Xie, \textit{et al.}", ``Study of Data-Driven Methods for Estimation of Fake Lepton Backgrounds", 
CMS AN-2009/120.

\bibitem{fakeLeptonNote2}
W.~Andrews, \textit{et al.}, ``Fake Rates for dilepton Analyses", CMS AN-2010/257.

\bibitem{fakeLeptonBkgSpillage1}
 F. Golf, D. Evans, J. Mulmenstadt  \textit{et al.}, ``Expectations for observation of top quark pair 
 production in the dilepton final state with the early CMS data'', CMS AN-2009/050.

\bibitem{dyestnote}
W. Andrews, et al., A Method to Measure the Contribution of $\dyll$ to a di-lepton+ MET Selection”, CMS AN-2009/023 (2009).

\bibitem{jes}
CMS Collaboration, ``Jet Energy Calibration with Photon+Jet Events", PAS JME-09-004.

\bibitem{jetpas}
CMS Collaboration, ``Jet Performance in pp Collisions at $\sqrt{s}=7 \rm\ TeV$", PAS JME-10-003.

\bibitem{mvajetid}
https://twiki.cern.ch/twiki/bin/view/CMS/PileupJetID

\bibitem{btag}
CMS collaboration, ``Commissioning of b-jet identification with pp collisions at $\sqrt{s}=7~\TeV$, BTV-10-001.

\bibitem{antikt}
Cacciari, Matteo and Salam, Gavin P. and Soyez, Gregory, ``The anti-$k_t$ jet clustering 
algorithm", JHEP 04,  2008.

\bibitem{ConversionNote}
W.~Andrews, \textit{et al.}, ``Study of photon conversion rejection at CMS", CMS AN-2009/159.

\bibitem{tmva}
A. Hoecker, \textit{et al.}, ``TMVA - Toolkit for Multivariate Data Analysis", arXiv:physics/0703039, 2007.

\bibitem{XS}
CMS Generator group, Standard Model Cross Sections for CMS at 7 TeV, 2010.

\bibitem{PDF4LHC}
PDF4LHC Working Group, 
{\tt http://www.hep.ucl.ac.uk/pdf4lhc/PDF4LHCrecom.pdf}.

\bibitem{Nadolsky:2008zw}
Nadolsky, Pavel M. and others, ``Implications of CTEQ global analysis for 
collider observables", Phys. Rev. D78 2008.

\bibitem{Martin:2009iq}
Martin, A. D. and Stirling, W. J. and Thorne, R. S. and Watt, G., ``Parton 
distributions for the LHC, Eur. Phys. J. C63 2009.

\bibitem{Ball:2010de}
Ball, Richard D. and others, ``A first unbiased global NLO determination 
of parton distributions and their uncertainties", arXiv 1002.4407.

\bibitem{bayesian}
A. O'Hagan and J.J. Forster, ``Bayesian Inference", Kendall's Advanced Theory of Statistics, 
Arnold, London, 2B, 2004.

\bibitem{ref:tagprobe_mit_w}
G. Bauer {\it et. al.}, ``Lepton ef?iencies for the inclusive W cross section measurement with 36.1pb$^{-1}$", AN2011/097.

\bibitem{ref:tagprobe_snt_top}
W. Andrews {\it et. al.}, ``Uncertainties on the Lepton Selection Efficiency for t$t\bar{t}$ Cross Section Analysis", AN2010/274.

\bibitem{ref:egamma_eff_gsf}
David Sabes, ``Electron reconstruction efficiency'', \\
{\small https://indico.cern.ch/getFile.py/access?contribId=2\&resId=0\&materialId=slides\&confId=140397}.

\bibitem{LHCHiggsCrossSectionWorkingGroup:2011ti}
LHC Higgs Cross Section Working Group, ``Handbook of LHC Higgs Cross Sections: 
Inclusive Observables", CERN-2011-002, 2011.

\bibitem{PFMET} 
CMS Collaboration, ``CMS MET Performance in Events Containing Electroweak Bosons from pp Collisions at $\sqrt{s}=7$ TeV'', CMS PAS JME-2010-005 (2010).

\bibitem{xyShiftMetCorr} 
{\small https://twiki.cern.ch/twiki/bin/view/CMSPublic/WorkBookMetAnalysis\#MET\_x\_y\_Shift\_Correction\_for\_mod}

\bibitem{trkMET} 
M.~Zanetti, ``MET with PU in $\hww \to 2\ell 2\nu$'', \\
https://indico.cern.ch/conferenceDisplay.py?confId=131580; 
B.~Hooberman, ``MET with PU in MC and First 2011 Data'', https://indico.cern.ch/contributionDisplay.py?contribId=5\&confId=132579. 

\bibitem{dymva}
L. Bauerdick, {\it et. al.}, ''A multivariate approach for Drell-Yan rejection in $\hww$ analysis", AN2012/210.

\bibitem{newdymva}
G.~Cerati, ``DYMVA training for HCP'', \\{\small https://indico.cern.ch/getFile.py/access?contribId=45\&sessionId=0\&resId=0\&materialId=slides\&confId=208848}

\bibitem{lands}
Mingshui Chen and Andrey Korytov, https://mschen.web.cern.ch/mschen/lands/.

\bibitem{MCFMHiggsProduction}
J. Campbell, R.K. Ellis, G. Zanderighi, ``Next-to-Leading order Higgs + 2 jet production via gluon fusion.'', JHEP 0610:028 (2006), hep-ph/0608194.

\bibitem{MCFMVVProduction}
J. Campbell, R.K. Ellis, C. Williams, ``Vector boson pair production at the LHC.'', arxiv:hep-ph/1105.0020.

\bibitem{jags}
M. Plummer, ``Jet Another Gibbs Sampler'', http://www-ice.iarc.fr/\~martyn/software/jags/.

\bibitem{MVASyst}
W. Andrews {\it et. al.}, ``Shape analysis for Higgs searches in di-lepton final state", 
CMS AN2011/408.

\bibitem{singleTopInterference}
J. Campell, F. Tramontano, ``Next-to-leading order corrections to Wt production and decay'', arxiv:hep-ph/0506289.

\bibitem{singleTopRemoval}
C.D. White, S. Frixione, E. Leanen, F. Maltoni {\it et. al.}, ``Isolating Wt production at the LHC'', arxiv:hep-ph/0908.0631.

\bibitem{wgstar}
  R.~C.~Gray, C.~Kilic, M.~Park, S.~Somalwar and S.~Thomas,
  ``Backgrounds To Higgs Boson Searches from Asymmetric Internal Conversion'',
  arXiv:1110.1368 [hep-ph].

\bibitem{rootstat}
L. Moneta et. {\it al.}, ``The RooStats Project", Proceedings of ACAT2010 conference, 2010.

\bibitem{cls1}
T. Junk, ``Confidence level computation for combining searches with small statistics'', 
Nucl.Instrum.Meth. {\bf A434} (1999) 435–443, arXiv:hep-ex/9902006. 
doi:10.1016/S0168-9002(99)00498-2.

\bibitem{cls2}
A. L. Read, ``Modified frequentist analysis of search results (the CLs method)'', 
CERN Yellow Report CERN-2000-005 (2000) 81.

\bibitem{cls_lhc}
ATLAS Collaboration, CMS Collaboration, and LHC Higgs Combination Group, 
``Procedure for the LHC Higgs boson search combination in summer 2011'', (July, 2011)

\bibitem{MENote}
W.~Andrews, et al., {Matrix Element based searches for Standard Model Higgs Boson in di-lepton final states with Full2011 dataset}, CMS AN-2011/489 (2011).

\bibitem{ZetaNote}
L.~Bauerdick, et al., {Estimating the Drell-Yan Contribution to a Dilepton + MET Selection using Photon+Jets Events in HWW Analysis}, CMS AN-2012/209 (2012).

\bibitem{ichep2012Note}
L.~Bauerdick, et al., {A Higgs Boson Search in the Fully Leptonic \WW final State}, CMS AN-2012/228 (2012).

\bibitem{2DNote}
L.~Bauerdick, et al., {A 2-dimensional Shape Analysis for the Higgs Boson Search in the Fully Leptonic \WW Final State}, CMS AN-2012/369 (2012).

\bibitem{hcp2012Note}
L.~Bauerdick, et al., {A Higgs Boson Search in the Fully Leptonic \WW final State}, CMS AN-2012/386 (2012).

\bibitem{spinNote}
L.~Bauerdick, et al., {The Spin of a Single Produced Resonance in the Fully Leptonic \WW Final State}, CMS AN-2012/453 (2012).

\bibitem{AcceptUncert}
G.~Bauer, et al., {Acceptance uncertainties for the inclusive W and Z cross section measurements}, CMS AN-2011/055 (2011).
