There are four processes which need to be estimated from Monte Carlo 
simulation, after applying the proper data corrections for lepton, trigger 
and jet veto efficiencies, in this low luminosity regime: $WZ$, 
$ZZ$, $W+\gamma$, $\dytt$.

$WZ$ and $ZZ$ backgrounds are partially estimated from data when the
two selected leptons are coming from the same $Z$ boson, together with
the $Z+jets$ process. Nevertheless, if the leptons are coming from
different bosons, we need to use the Monte Carlo expectations to
account for them since that contribution is not included. We should
emphasize that those contributions are expected to be rather
small, as explained in Section~\ref{sec:sel_other}.

The $W+\gamma$ background, where the $\gamma$ decays into an
electron-positron pair, is difficult to estimate from data in addition 
to cross-checks that can be performed. For instance, applying the
same standard selection, but requiring two same-sign leptons, gives a
sample dominated by $\Wjets$ and $W+\gamma$ events. Again, we should
emphasize that the expected contribution is very small, thanks to the
stringent $\gamma$ conversion requirements explained in
Sec.~\ref{sec:sel_electrons}.

The $\dytt$ background, where both $\tau$ leptons decays into the $\Lep\Nu\Nu$ 
final state, is difficult to estimate directly from data since it does not 
show a resonant mass peak distribution. Nevertheless, both the leptonic 
branching ratios and cross-section are well-known, and the process is 
relatively clean with two leptons in the final state. Hence, we can rely on 
the Monte Carlo expectations to estimate this background. In addition, the 
expected contribution is rather small thanks to the $\met$ requirements and 
the relatively soft leptons from the $\tau$ decays.

The contribution for all these processes after all $\WW$-like requirements is given 
in Tabables.~\ref{tab:diboson_bck0j},~\ref{tab:diboson_bck1j} and~\ref{tab:diboson_bck2j} 
for the three different jet bins.

\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
		 &  \multicolumn{4}{|c|}{process}    \\
 final state	 &  $W+\gamma$ & $WZ$ & $ZZ$ & $\dytt$  \\
\hline
$\mu\mu$	 &  0.15 $\pm$ 0.13 & 1.97 $\pm$ 0.07 & 0.03 $\pm$ 0.01 & 0.00 $\pm$ 0.00 \\
$ee$  	         &  1.17 $\pm$ 0.18 & 1.12 $\pm$ 0.11 & 0.02 $\pm$ 0.01 & 0.00 $\pm$ 0.00 \\
$e\mu$	         &  7.98 $\pm$ 1.50 & 5.89 $\pm$ 0.24 & 0.09 $\pm$ 0.01 & 1.51 $\pm$ 1.51 \\
\hline
Total	         &  9.30 $\pm$ 1.62 & 8.98 $\pm$ 0.29 & 0.14 $\pm$ 0.02 & 1.51 $\pm$ 1.51 \\
\hline
\end{tabular}
\caption{Summary of the background contributions for $W+\gamma$, $WZ$ ,$ZZ$ 
and $\dytt$ processes in the 0-jet bin for the $\WW$-like selection, including 
the Monte Carlo statistical uncertainty\label{tab:diboson_bck0j}.}
\end{center}
\end{table}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
		 &  \multicolumn{4}{|c|}{process}    \\
 final state	 &  $W+\gamma$ & $WZ$ & $ZZ$ & $\dytt$  \\
\hline
$\mu\mu$	 &  1.98 $\pm$ 0.48 & 0.97 $\pm$ 0.07 & 0.00 $\pm$ 0.00 & 0.00 $\pm$ 0.00 \\
$ee$  	         &  0.49 $\pm$ 0.14 & 1.05 $\pm$ 0.08 & 0.00 $\pm$ 0.00 & 0.00 $\pm$ 0.00 \\
$e\mu$	         &  1.12 $\pm$ 0.31 & 5.16 $\pm$ 0.22 & 0.07 $\pm$ 0.02 & 8.68 $\pm$ 3.32 \\
\hline
Total	         &  3.59 $\pm$ 0.56 & 7.19 $\pm$ 0.26 & 0.07 $\pm$ 0.02 & 8.68 $\pm$ 3.52 \\
\hline
\end{tabular}
\caption{Summary of the background contributions for $W+\gamma$, $WZ$ ,$ZZ$ 
and $\dytt$ processes in the 0-jet bin for the $\WW$-like selection, including 
the Monte Carlo statistical uncertainty\label{tab:diboson_bck1j}.}
\end{center}
\end{table}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
		 &  \multicolumn{4}{|c|}{process}    \\
 final state	 &  $W+\gamma$ & $WZ$ & $ZZ$ & $\dytt$  \\
\hline
$\mu\mu$	 &  0.80 $\pm$ 0.12 & 0.17 $\pm$ 0.02 & 0.00 $\pm$ 0.00 &  0.00 $\pm$ 0.00  \\
$ee$  	         &  1.00 $\pm$ 0.41 & 0.30 $\pm$ 0.03 & 0.00 $\pm$ 0.00 &  0.00 $\pm$ 0.00  \\
$e\mu$	         &  0.09 $\pm$ 0.09 & 1.12 $\pm$ 0.05 & 0.01 $\pm$ 0.01 &  6.00 $\pm$ 1.53  \\
\hline
Total	         &  1.89 $\pm$ 0.47 & 1.59 $\pm$ 0.14 & 0.01 $\pm$ 0.01 &  6.00 $\pm$ 1.53 \\
\hline
\end{tabular}
\caption{Summary of the background contributions for $W+\gamma$, $WZ$ ,$ZZ$ 
and $\dytt$ processes in the 0-jet bin for the $\WW$-like selection, including 
the Monte Carlo statistical uncertainty\label{tab:diboson_bck2j}.}
\end{center}
\end{table}
