
This appendix describes the ''reload`` of the analysis described in the body
of this document with additional data for the Lepton Photon 2011 conference.
The reload primarily adds extra data to the existing analysis, but also 
includes minor technical changes described in this appendix.
We define the following naming conventions for the analyses described:

\begin{itemize}
    \item The EPS analysis refers to the methods and results documented in the body of this note.
    \item The LP analysis refers to the application of the EPS analysis methods to the extended dataset.
\end{itemize}

We define the following naming conventions for the datasets used:

\begin{itemize}
    \item The EPS dataset refers to the initial \intlumi dataset.
    \item The post-EPS dataset refers to the ~ 0.5 fb$^-1$ dataset recorded after the EPS2011 conference.
    \item The LP dataset refers to the total \lpintlumi dataset.
\end{itemize}

We performed this reload according to the following methodology:

\begin{itemize}
    \item We first identified a number of necessary but small technical changes to the analysis.  
These are summarised in Section \ref{sec:lp_technical_changes}.
    \item We then validated these changes by performing a side by side comparison of 
the analysis on the EPS dataset with and without these changes.
These are summarised in Section \ref{sec:lpreload_technical_validation}.
Having convinced ourselves that the analysis was understood, we proceeded to add more data.
    \item We first validated the post-EPS dataset against the existing results for the EPS dataset.
We found good agreement in the background estimates and data to simulation scale factors.
    \item We then performed the background estimations and full analysis on the LP dataset.
The results of the reloaded analysis are described in Section \ref{sec:lpreload_results}.
\end{itemize}

