\documentclass{cmspaper}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage[pdfborder=0 0 0,
            colorlinks,
            urlcolor = blue,
            linkcolor = black,
            citecolor = black,
            menucolor = black,]
           {hyperref}
%% \usepackage[colorlinks]{hyperref}
%% \usepackage{url}
\usepackage[toc,page]{appendix}
\renewcommand{\appendixname}{Appendix}
%% \renewcommand{\appendixtocname}{List of appendices}

% \input{privsym}
\input{commands}

\setcounter{topnumber}{1}
\setcounter{bottomnumber}{1}

\begin{document}
\begin{titlepage}

  \analysisnote{2011/XXX}

  \date{\today}

  \title{Search for Higgs Boson in the Fully Leptonic $W^+W^-$ Final State}

  \begin{Authlist}
  \end{Authlist}

  % if needed, use the following:
  \collaboration{CMS collaboration}

  % \Anotfoot{a}{On leave from prison}
  %\Anotfoot{b}{Now at the Moon}
  \begin{abstract}
    This note describes a search for the Higgs boson in $\WW \to 2\ell2\nu$
    final state with 49~pb$^{-1}$ of $pp$ collision data at $\sqrt s =
    $ 7~$\TeV$. We search for Higgs candidate events in $ee$, $\mu\mu$ and $e\mu$
    channels with 0, 1 and 2 reconstructed jets in the final state. Signal and
    background yields are extrapolated to 1 $\ifb$ of collected data to obtain
    sensible projections.
  \end{abstract} 

\end{titlepage}
\tableofcontents
%\listoftables
%\listoffigures
\newpage 

\section{Introduction}
  \label{sec:overview}
  \input{introduction}
  
\section{Data Samples}
  \label{sec:datasets}
  \input{datasets}
  
\section{Event Selection}
  \label{sec:selection} 
  \input{selection_introduction}
  \subsection{Trigger}
    \label{sec:sel_trigger}
    \input{selection_trigger}
  \subsection{Primary Vertex Reconstruction}
    \label{sec:sel_pv}
    \input{selection_pv}
  \subsection{Muon Selection} 
    \label{sec:sel_muons}
   \input{selection_muons}
  \subsection{Electron Selection} 
    \label{sec:sel_electrons}
    \input{selection_electrons}
  \subsection{Missing Energy} 
    \label{sec:sel_met}
    \input{selection_met}
  \subsection{$Z$ Veto}
    \label{sec:sel_zveto}
    \input{selection_zveto}
  \subsection{Jet Counting} 
    \label{sec:sel_jets}
    \input{selection_jets}
  \subsection{Top Tagging}
    \label{sec:sel_toptag}
    \input{selection_toptag}
  \subsection{Other Preselection Requirements}
    \label{sec:sel_other}
    \input{selection_other}

\section{Event yields in Data and Monte Carlo}
  \label{sec:yields}
  \input{yields_mc}
    
\section{Signal Extraction}
  \input{selection_intro}
  \label{sec:signal_selection}
  \subsection{Cut Based Analysis}
    \label{sec:anal_cutbased}
    \subsubsection{0-Jet Selection}
      \label{sec:sel_zerojet}
      \input{selection_zerojet}
    \subsubsection{1-Jet Selection}
      \label{sec:sel_onejet}
      \input{selection_onejet}
    \subsubsection{VBF Selection}
      \label{sec:sel_vbf}
      \input{selection_vbf}
  \subsection{MVA Analysis}
    \label{sec:anal_mva}
    \input{anal_mva}
%  \subsection{Matrix Element Method}
%    \label{sec:anal_me}
%    \input{anal_me}

\clearpage
\section{Background Estimation}
    \label{sec:backgrounds}
    \input{bkg_intro}
    \label{sec:bkg_intro}
  \subsection{WW Background}
    \label{sec:bkg_ww}
    \input{bkg_ww}
  \subsection{Jet Induced Backgrounds}
    \label{sec:bkg_fakes}
    \input{bkg_fakes}
  \subsection{Top Background}
    \label{sec:bkg_top}
    \input{bkg_top}
  \subsection{Drell-Yan Background}
    \label{sec:bkg_dy}
    \input{bkg_dy}
  \subsection{Other Backgrounds}
    \label{sec:bkg_other}
    \input{bkg_other}

\section{Efficiency Measurements}
   \input{eff_intro}
      \label{sec:efficiency}
   \subsection{Electron Efficiency}
      \input{eff_electron}
      \label{sec:eff_electron}
   \subsection{Muon Efficiency}
      \input{eff_muon}
     \label{sec:eff_muon}
        \subsection{Trigger Efficiency}
      \input{eff_trigger}
      \label{sec:eff_trigger}
   \subsection{Jet Efficiency}
      \input{eff_jet}

\section{Systematic Uncertainties}
  \label{sec:systematics}
  \input{systematics}

\section{Sensitivity Projections with 1~$\ifb$}
  \label{sec:results}
  \input{results}

\section{Data Results with 49~$\ipb$}
  \label{sec:dataresults}
  \input{data_results}

\section{Summary}
    \label{sec:summary}
    \input{summary}

\clearpage

\vspace*{-0.2cm}
\thebibliography{12}

\bibitem{pdg}
 K. Nakamura et al. (Particle Data Group), "Review of particle physics", J. Phys.G37 , 2010.

\bibitem{Higgs1}
F. Englert and R. Brout, "Broken symmetries and the masses of gauge bosons", Phys. Rev. Lett. 13,  1964.

\bibitem{Higgs2}
P. W. Higgs, "Broken symmetry and the mass of gauge vector mesons", Phys. Rev. Lett. 13, 1964.

\bibitem{Higgs3}
Guralnik, G.S. and Hagen, C.R. and Kibble, T.W.B., "Global Conservation Laws and Massless Particles", 
Phys.Rev.Lett. 13, 1964.

\bibitem{HWW2010}
CMS Collaboration, "Title: Measurement of WW Production and Search for the Higgs Boson in 
pp Collisions at $\sqrt{s}$ = 7 TeV", arXiv:1102.5429

\bibitem{VBTFCrossSectionNote}
J. Alcaraz Maestre, \textit{et al.}, "Updated Measurements of Inclusive W and Z Cross Sections 
at $\sqrt{s}=7$ TeV", CMS AN-2010/264.

\bibitem{ggWWError}
F.~ Stoeckli, "http://indico.cern.ch/getFile.py/access?contribId=0\&resId=1\&materialId=slides\&confId=49009", 
EWK Diboson meeting of March 12 2009.

\bibitem{json}
Hand made version for now

\bibitem{ElIso}
A. Vartak, M. LeBourgeois, V. Sharma, "Lepton Isolation in the CMS Tracker, ECAL and HCAL", CMS AN-2010/106.

\bibitem{NExpHits}
B. Mangano \textit{et al.}, "Improvement in Photon Conversion Rejection Performance Using 
Advanced Tracking Tools", AN-10-283.

\bibitem{fakeLeptonNote1}
S.~Xie, \textit{et al.}", "Study of Data-Driven Methods for Estimation of Fake Lepton Backgrounds", 
CMS AN-2009/120.

\bibitem{fakeLeptonNote2}
W.~Andrews, \textit{et al.}, "Fake Rates for dilepton Analyses", CMS AN-2010/257.

\bibitem{jes}
CMS Collaboration, "Jet Energy Calibration with Photon+Jet Events", PAS JME-09-004.

\bibitem{jetpas}
CMS Collaboration, "Jet Performance in pp Collisions at $\sqrt{s}=7 \rm\ TeV$", PAS JME-10-003.

\bibitem{btag}
CMS collaboration, "Commissioning of b-jet identification with pp collisions at $\sqrt{s}=7~\TeV$, BTV-10-001.

\bibitem{antikt}
Cacciari, Matteo and Salam, Gavin P. and Soyez, Gregory, "The anti-$k_t$ jet clustering 
algorithm", JHEP 04,  2008.

\bibitem{ConversionNote}
W.~Andrews, \textit{et al.}, "Study of photon conversion rejection at CMS", CMS AN-2009/159.

\bibitem{tmva}
A. Hoecker, \textit{et al.}, "TMVA - Toolkit for Multivariate Data Analysis", arXiv:physics/0703039, 2007.

\bibitem{XS}
CMS Generator group, Standard Model Cross Sections for CMS at 7 TeV, 2010.

\bibitem{PDF4LHC}
PDF4LHC Working Group, 
{\tt http://www.hep.ucl.ac.uk/pdf4lhc/PDF4LHCrecom.pdf}

\bibitem{Nadolsky:2008zw}
Nadolsky, Pavel M. and others, "Implications of CTEQ global analysis for 
collider observables", Phys. Rev. D78 2008.

\bibitem{Martin:2009iq}
Martin, A. D. and Stirling, W. J. and Thorne, R. S. and Watt, G., "Parton 
distributions for the LHC, Eur. Phys. J. C63 2009.

\bibitem{Ball:2010de}
Ball, Richard D. and others, "A first unbiased global NLO determination 
of parton distributions and their uncertainties", arXiv 1002.4407.

\bibitem{bayesian}
A. O'Hagan and J.J. Forster, "Bayesian Inference", Kendall's Advanced Theory of Statistics, 
Arnold, London, 2B, 2004.

\bibitem{ref:tagprobe_mit_w}
G. Bauer {\it et. al.}, "Lepton efﬁciencies for the inclusive W cross section measurement with 36.1pb$^{-1}$", AN2011/097

\bibitem{ref:tagprobe_snt_top}
W. Andrews {\it et. al.}, "Uncertainties on the Lepton Selection Efficiency for t$t\bar{t}$ Cross Section Analysis", AN2010/274


\appendix
\appendixpage
  \section{Primary Vertex Reweighting}
     \label{app:vertex_reweight}
     \input{appendix_vertex_reweight}
  \clearpage
  \section{Electron Selection Optimization}
     \label{app:els}
     \input{appendix_els}
  \clearpage
  \section{Muon Selection Optimization}
     \label{app:mus}
     \input{appendix_mus}
  \clearpage
%  \section{$\met$ Options}
%     \label{app:met}
%     \input{appendix_met}
  \clearpage
  \section{Online vs Offline Selection}
     \label{app:online_vs_offline}
     \input{appendix_online_vs_offline}
  \clearpage
  \section{Fake Rate Studies}
     \label{app:fake_rate_studies}
     \input{appendix_muon_fakes}
     \input{appendix_electron_fakes}
  \section{Pileup Effect on Isolation}
     \label{app:PUIso}
     \input{appendix_PUIso}
%%   \section{Electron selection details}\label{sec:eledetail}
%%     \input{electron_detail}
%%   \section{Using the transverse mass of the $W$ for
%%     \dytt\ suppression}\label{sec:mt} 
%%     \input{mt}
%%   \section{Jet Veto at high $\eta$}
%%     \input{higheta}
%%   \section{Jet Veto using $b$ tagging}
%%     \input{btagging}
%%   \section{Application of the Drell-Yan estimate method}
%%     \label{app:dy22X}
%%     \input{drell_yan_appendix}
%%   \section{Event yields in other samples}
%%     \label{app:othersamples}
%%     \input{alt_samples}
%%   \section{Estimating the sensitivity to observe \ww\ in 100/pb}
%%     \label{app:significance}
%%     \input{significance}
%%   \section{QCD multi jet background estimation}
%%     \label{app:qcd}
%%     \input{qcd}
%% \input{biblio}

\end{document}
