Muons in CMS are reconstructed as either $StandAloneMuons$ (track
in the muon detector with low momentum resolution), $GlobalMuons$
(outside-in approach seeded by a $StandAloneMuon$ with a global fit
using hits in the muon, silicon strip and pixel 
detectors) and $TrackerMuons$ (inside-out approach seeded by an offline 
silicon strip track, using the muon detector only for muon identification 
without refitting the track). Most good quality muons are reconstructed as 
all three types at the same time and the momentum resolution is dominated by the inner
tracker system up to about 200~$\GeVc$ in transverse momentum. Details about the
optimization at low $\pt$ are given in Appendix~\ref{app:mus}. The specific
requirements to select good prompt isolated muons are the following:
\begin{itemize}
\item the muon must be found by both the global and tracker muon algorithms;
\item the global muon must have at least one good muon hit;
\item the tracker muon must have at least two matches to muon segments in 
      different muon stations;
\item more than 10 hits in the inner tracker;
\item at least one pixel hit;
\item $\chi^2/{\mathrm{ndof}} < 10$ on a global fit;
\item impact parameter in the transverse plane $|d_{0}| < 0.02~(0.01)$~cm for
      muons with $\pt$ greater (smaller) than 20 $\GeVc$,
      calculated with respect to the primary vertex;
\item longitudinal impact parameter $|d_{z}| <0.2$~cm,
      calculated with respect to the primary vertex;
\item pseudorapidity $|\eta|$ must be smaller than 2.4;
\item relative \pt\ resolution is better than 10\%.
\end{itemize}

Furthermore, tracker- and calorimeter- based isolation variables are
used to reduce the contamination from the non-isolated muons originating from
jets. We use a combination of tracker, ECAL and HCAL
based isolation:

\begin{itemize}
\item $\rm{Iso}_{Track}$: defined as the scalar sum of the \pt\ of the 
    tracks in a 0.01$~<~\Delta R~<~$0.3 cone around the muon
    in the $\eta \times \phi$ plane;

\item $\rm{Iso}_{ECAL}(\rm{Iso}_{HCAL})$: defined as the 
    scalar sum of the transverse energy of the calorimeter ECAL (HCAL) towers 
    in a $\Delta R$ cone of 0.3 centered on the muon with a veto cone of 
    $\Delta R = 0.01 $ around it.
\end{itemize}

The combined isolation variable is defined as 
$\rm{Iso}_{Total} = \rm{Iso}_{Track}+\rm{Iso}_{ECAL}+\rm{Iso}_{HCAL}$, 
and we require $\frac{\rm{Iso}_{Total}}{\pt}~<~0.15~(0.10)$ for muons 
with $\pt$ greater (smaller) than 20 $\GeVc$.


The presence of pileup introduces additional energy into the isolation cone.
This is expected to reduce the efficiency of the isolation cut as the amount of 
pileup increases. The average efficiency loss for signal muons for with $p_{T} > 20$ GeV, 
during current running conditions, is 
found to be approximately $1\%$, estimated using $\hww$ (with $m_H=130\GeVcc$) signal MC. 
One specific procedure to correct for pileup contributions to the
isolation sum is referred to as the fastjet correction method.
This was investigated and found to over-correct the isolation and increase the
efficiency on background electrons, giving comparatively worse performance.
Therefore we currently do not perform any pileup corrections for isolation while
we continue to investigate other options.
This is discussed in more detail in Appendix \ref{app:PUIso}.

